---
title: "Discrimination in Salary"
author: 
  - Gulamzada, Aysel[^1]
bibliography: ../bibliography/biblio.bib
csl: ../csl/apa.csl
header-includes:
  - \usepackage{polyglossia}
  - \setmainlanguage{english}
  - \usepackage{booktabs}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=10pt}
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: no
    latex_engine: xelatex
    number_sections: yes
    toc: no
geometry: margin=1in
link-citations: yes
urlcolor: blue
fontsize: 12pt
biblio-style: apalike
abstract: |
    Write your abstract here.
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

<!-- ======================================================================= -->
<!-- ============================== FOOTNOTES ============================== -->
<!-- ======================================================================= -->
[^1]: 21080060, [Github Repo](https://github.com/ayselgulamzada/21080060)


# Introduction

Earnings differentials among employees based on sex and economic activity are critical aspects of socioeconomic inequality that require careful examination. This paper investigates the variations in mean nominal monthly earnings among employees across different regions, specifically focusing on the influence of sex and economic activity. By exploring these factors, this study aims to contribute to our understanding of global wage disparities and inform policies and strategies for promoting fair and equitable employment practices.

Gender-based wage gaps have been a subject of considerable concern and research. In addition to being essential for social justice, achieving gender equality in the workforce is critical for sustainable development. This paper takes a global perspective, examining gender wage differences across multiple regions worldwide, in contrast to earlier research limited to specific nations or sectors.

In addition to gender, economic activity plays a significant role in determining earnings disparities. Different sectors and industries offer distinct remuneration structures, leading to variations in earnings levels. By considering economic activity as a critical variable, this study aims to understand how mean nominal monthly earnings differ across sectors within different regions. Analyzing these variations provides valuable information about industries where profits are exceptionally high or low, shedding light on potential drivers of inequality.

The central research question guiding this study is "How do the mean nominal monthly earnings of employees vary by sex and economic activity (in local currency) in different regions of the world?". The Data set was taken from Labour Force Statistics. The dataset contains 627 observations and 12 variables. The findings of this research have important implications for policymakers, organizations, and advocacy groups committed to promoting fair and inclusive labor practices globally.

## Literature Review

Discrimination in salaries based on sex is a persistent and concerning issue in many societies. Numerous studies have highlighted the existence of a gender wage gap, where women tend to earn less than their male counterparts for similar work. This disparity not only has significant economic implications but also reflects deep-rooted gender inequalities in the labor market. Understanding the extent and underlying causes of this wage gap is crucial for developing effective policies and initiatives to promote gender equality in employment.

@barbezat:1987 provides estimates of both total differentials and salary discrimination between males and females. @jena:2016 undertakes an analysis of sex differences in academic physician salary that was designed to mitigate many of the limitations of previous studies on this topic. @belon:1977 the larger proportion of women than men being employed at lower-paying institutions coupled with the fact that women were most likely to be found on the lower end of the academy ladder. @robert:1983 employer discrimination is a principal source of discrimination against blacks and women, then we would expect the female/male earnings ratios to be higher for the self-employed compared to their wage and salary counterparts. @larson:2014 aims to develop and test hypotheses on determinants of supply chain managers’ salaries. While women make up about half the workforce, there is evidence in the trade press that they receive far less than half of the compensation. Sex of the manager and size of his or her organization are among the predictors of salary. @gollob:1984 the difference index defines sex bias as the difference in mean salary inequities between men and women and emphasizes the necessity of deciding how much relevant differences in qualifications are worth.

# Data

```{r code_chunk_name, echo = FALSE}

library(tidyverse)

library(here)

survey <- read_csv(here("data/Employment.csv"))

```


```{r, echo=FALSE}
library(xtable)
library(summarytools)
st_options(lang = "en")
```


```{r results='asis', echo=FALSE}
survey %>% 
  select("Manufacturing", "Construction", "Agriculture", "Mining and quarrying; Electricity, gas and water supply", "Public Administration, Community, Social and other Services and Activities") %>%
  descr(stats = c("mean", "sd", "min", "med", "max"), transpose = TRUE) %>%
  xtable(caption = "Summary Statistics",
         label = "tab:summary",
         align = c("l", "c", "c", "c", "c", "c")) %>%
  print(booktabs = TRUE, comment = FALSE, caption.placement = "top")
```


# Methods and Data Analysis
In this section describe the methods that you use to achieve the purpose of the study. You should use the appropriate analysis methods (such as hypothesis tests and correlation analysis) that we covered in the class. If you want, you can also use other methods that we haven't covered. If you think some method is more suitable for the purpose of the analysis and the data set, you can use that method [@newbold:2003; @verzani:2014; @wickham:2014; @wooldridge:2015a].

For example, if you are performing regression analysis, discuss your predicted equation in this section. Write your equations and mathematical expressions using $LaTeX$.

$$
Y_t = \beta_0 + \beta_N N_t + \beta_P P_t + \beta_I I_t + \varepsilon_t
$$

This section should also include different tables and plots. You can add histograms, scatter plots (such as Figure \@ref(fig:plot)), box plots, etc. Make the necessary references to your figures as shown in the previous sentence.




# Conclusion
Summarize the results of your analysis in this section. Discuss to what extent your results responded to the research question you identified at the beginning and how this work could be improved in the future.

**References section is created automatically by Rmarkdown. There is no need to change the references section in the draft file.**

**_You shouldn't delete the last 3 lines. Those lines are required for References section._**

\newpage
# References {#references}
<div id="refs"></div>

